---
title: "Alcohol vs Seat choice"
author: "Matthew Diaz"
date: "2-12-2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

The research question is this: Is there a difference in the amount of alcohol consumed per week by students who sit in row 1, row 2, or row 3 of the UC Davis classroom.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Methods 

We are trying to predict alcohol consumption based o seating row. 

Data Form UC Davis:

alcohol ~ Seat

alcohol is a numerical variable

seat is a categorical variable

So we use the numerical~cat helper file.

# Description

## Graphical description

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

## numerical description

## inferential description

## Conclusions and Discussion


