---
title: "Alcohol vs Seat choice"
author: "Matthew Diaz"
date: "2-12-2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

The research question is this: Is there a difference in the amount of alcohol consumed per week by students who sit in row 1, row 2, or row 3 of the UC Davis classroom.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Methods 

We are trying to predict alcohol consumption based o seating row. 

Data Form UC Davis:

alcohol ~ Seat

alcohol is a numerical variable

seat is a categorical variable

So we use the numerical~cat helper file.

# Description

## Graphical description

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

This box plot shows us that there is a significant difference in the back rows consumption in alcohol compared to the middle and back rows. Based on the box plot, students in the back row seem to be consuming more alcohol. 

## numerical description
```{r}
favstats(alcohol~Seat,data=davisdata)
```

Based on the table, the back row has a mean of 9.6, the front row has a mean of 1.8, and the middle row has a mean of 3.2. Apparently, students in the back row tend to drink more.

## inferential description

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p value is 0.000116. That means the students in all the rows do not consume the same amount of alcohol. 

```{r}
plot(TukeyHSD(model1))
```

From the Tukey HSD test we found that people seated in the back row drink more than people drinking in the middle and front rows. There is no difference in alcohol consumption between the middle and front rows. 

## Conclusion

We are trying to see if there is a difference in students who consume alcohol in rows 1, 2, 3. The p-value is 0.000116 which is less than 0.05 which means we reject the null hypothesis. Once we read the graph given to us by the Tukey HSD model, it is understood that students in the back row drink more alcohol than the middle and front row.
